---
title: 'Code snippet to the paper: <br> Switching between different non-hierarchical administrative
  areas via simulated geo-coordinates: A case study for student residents in Berlin'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RColorBrewer)
```

## Case of application

The proposed method is useful for a situation where counts for a specific regional 
level are available with their geocoordinates but the distribution on another regional 
level is of interest.

In the application described in the paper "Switching between different non-hierarchical 
administrative areas via simulated geo-coordinates: A case study for student residents in Berlin" 
the numbers of students is known for the zip code level but the administration is 
interested in the distribution of students on a smaller regional level that is 
used for urban planning in Berlin, the so-called "Lebensweltlich-orientierte Räume (LOR)". 


## Data source and shape files

The data that is available is the number of students by zip code and the latitude
and longitude of the center of the zip code areas. Please note that the data used
in this example is random data for the student count so the results cannot be 
used for any analysis.

```{r data}
dataZip <- read.csv("dataZip.csv", sep = ";")
head(dataZip)
```

Furthermore, the shape file for the zip codes is needed. 

```{r shapeZIP, warning=FALSE, message=FALSE}
library(rgeos)
shapefileZip <- rgdal::readOGR("RBS_OD_PLZ_2014.shp", layer="RBS_OD_PLZ_2014")
plot(shapefileZip)
```


## Estimation

With the dshapebivr function of the R package Kernerlheaping, the bivariate kernel 
density is estimated using the available data on zip code level and the shape file.

```{r kernelDensity, warning=FALSE, message=FALSE}
library(Kernelheaping)
Mestimates <- dshapebivr(data=dataZip, burnin=1, samples=5, shapefile= shapefileZip, 
                         gridsize = 50, boundary = TRUE)
```

Another example up to this point is the [estimation of the density of inhabitants between a specific age group](https://www.inwt-statistics.com/read-blog/introducing-the-kernelheaping-package-ii.html). For this
example, it is also shown [how to exclude uninhabited areas](https://www.inwt-statistics.com/read-blog/introducing-the-kernel-heaping-package-iii.html). 

The switching from the zip code level to the LOR level is provided by function 
toOtherShape. The arguments are the return of the dshapebivr function and a
shape file on the LOR level.


```{r, results='hide', message=FALSE}
shapefileLORS <- rgdal::readOGR("RBS_OD_LOR_1412.shp",layer="RBS_OD_LOR_1412")
LOREstimates <- toOtherShape(Mestimates = Mestimates, shapefile= shapefileLORS)
```

It returns the average density, standard deviation and the 0.05th and 0.95th 
quantile.

```{r}
head(LOREstimates)
```


```{r}
plot(shapefileLORS, col = brewer.pal(7, "OrRd")[as.numeric(cut(LOREstimates$meanCount,
                                                               c(0, 10, 20, 50, 100, 500, 1000, Inf),
                                                               include.lowest = TRUE))])
```

